Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} Stagnating State Funding for Higher Education and its Effect on Faculty

### 2024-01-03 text/paper.tex
writing revision (working on the final revision).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl.
        I thank seminar participants at Cornell University (2022, 2023) for helpful discussion.
        This project's repository, with all materials and anonymised data needed for replication, is available at 
        \url{https://github.com/shoganhennessy/state-funding-faculty}.
        Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\
    \vspace{0.1cm}
    Economics Department, Cornell University\footnote{
        Address: Uris Hall \#447, Economics Department, Cornell University NY 14853 USA.
    }
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    Stagnating State Funding for Higher Education and its Effect on Faculty}
\date{This version: \today \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding for Higher Education and its Effect on Faculty.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Starting the paper
\newpage
\setcounter{page}{1}
\doublespacing
% Introduction section
\noindent
\input{sections/01-introduction.tex}
% Data section
\input{sections/02-data.tex}
% Conceptual Framework
\input{sections/03-concepts.tex}
% Empirical methods
\input{sections/04-empirical.tex}
% Empirical results
\input{sections/05-results.tex}
% Dicussion
\input{sections/06-discussion.tex}
% Conclusion
\input{sections/07-conclusion.tex}
% Rev of Econ Ed Statements.
\subsubsection*{Data Statement}
Every source of data, and the code to fully replicate the entire analysis is freely available at the following link:
\url{https://github.com/shoganhennessy/state-funding-faculty}.
IBHED data, while public knowledge, include personally identifiable names, so the data included in the replication package have names replaced with non-identifiable placeholders.
\subsubsection*{Credit Author Statement}
As the only author on this paper, I am responsible for all contributions in this paper.
\subsubsection*{Declaration of Competing Interest}
This paper's author has no competing interests to declare.

% Bibliography
\singlespacing
\bibliographystyle{agsm}
\bibliography{sections/08-bibliography.bib}

% Separated Figures \& Tables
\newpage
\input{sections/09-figures-tables.tex}

% Appendix
\input{sections/10-appendix.tex}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl.
        I thank seminar participants at Cornell University (2022, 2023) for helpful discussion.
        This project's repository, with all materials and anonymised data needed for replication, is available at 
        \url{https://github.com/shoganhennessy/state-funding-faculty}.
        Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\
    \vspace{0.1cm}
    Economics Department, Cornell University\footnote{
        Address: Uris Hall \#447, Economics Department, Cornell University NY 14853 USA.
    }
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    Stagnating State Funding for Higher Education and its Effect on Faculty}
\date{This version: \today \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2024.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding for Higher Education and its Effect on Faculty.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Starting the paper
\newpage
\setcounter{page}{1}
\doublespacing
% Introduction section
\noindent
\input{sections/01-introduction.tex}
% Data section
\input{sections/02-data.tex}
% Conceptual Framework
\input{sections/03-concepts.tex}
% Empirical methods
\input{sections/04-empirical.tex}
% Empirical results
\input{sections/05-results.tex}
% Dicussion
\input{sections/06-discussion.tex}
% Conclusion
\input{sections/07-conclusion.tex}
% Rev of Econ Ed Statements.
\subsubsection*{Data Statement}
Every source of data, and the code to fully replicate the entire analysis is freely available at the following link:
\url{https://github.com/shoganhennessy/state-funding-faculty}.
IBHED data, while public knowledge, include personally identifiable names, so the data included in the replication package have names replaced with non-identifiable placeholders.
\subsubsection*{Credit Author Statement}
As the only author on this paper, I am responsible for all contributions in this paper.
\subsubsection*{Declaration of Competing Interest}
I have no competing interests to declare.
% Separated Figures \& Tables
\newpage
\input{sections/09-figures-tables.tex}
% Bibliography
\singlespacing
\bibliographystyle{agsm}
\bibliography{sections/08-bibliography.bib}
% Appendix
\input{sections/10-appendix.tex}
\end{document}
